Exposing Disputed Statements on the Web

### 2009-03-19 papers/uist_thinklink/thinklink.tex
Did related work on argumentation and accuracy checking

Cohere~\cite{Shum2008}. Compendium~\cite{Selvin2001}. Cope it~\cite{Karacapilidis2001}. AIF~\cite{McGinnis2007} and ArgDF~\cite{Rahwan2007}. IBIS~\cite{Rittel1973}. gIBIS~\cite{Conklin1987}. IBIS problems~\cite{Isenmann1997}. ClaimSpotter~\cite{Sereno2005,Sereno2004}. ClaiMaker~\cite{Uren2003}. Video Annotation~\cite{Diakopoulos2008}. Collabatorium~\cite{Klein2007}, for Global Warming~\cite{Malone2007}. Lawyer argument model~\cite{Verheij1999}. Toulmin model~\cite{Toulmin1958}. Zeno~\cite{Gordon1997}. Discoursium~\cite{Yetim2007}.
Entity Workspace~\cite{Billman2007}. 
Mess Maps and Resolution Mapping~\cite{Horn2007}.
TRELLIS~\cite{Chklovski2005}.  
People should define own link types~\cite{Wang1998}.

Hypertext systems such as Notecards~\cite{Halasz1988}.

\subsection{Checking Accuracy on the Web}

NewsCube~\cite{Park2009}.
Wikipedia fixes Vandalism~\cite{Viegas2004}.
Trustworthiness~\cite{Gil2006}.
WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.

@@

>>>>

Think Link is an example of an Issue Based Information System (IBIS)~\cite{Rittel1973}. IBIS tools such as gIBIS~\cite{Conklin1987}, Compendium~\cite{Selvin2001}, Collabatorium~\cite{Klein2007}, Zeno~\cite{Gordon1996}, and Cohere~\cite{Shum2008} model discouse as a graph of connected ideas. While the graph structure varies between tools, most tools allow one to mark an idea as supporting or opposing another idea, and allow one to mark an idea as addressing an issue. Some tools, such as Collabatorium~\cite{Klein2007} and Cope It~\cite{Karacapilidis2001} structure an argument as a tree, while others such as Think Link, gIBIS~\cite{Conklin1987} and Cohere~\cite{Shum2008} structure an argument as a graph, in which a single idea can support or oppose multiple other ideas.

Cohere is perhaps the tool most similar to Think Link. Cohere allows one to use snippets from web pages as evidence to support ideas in its argument graph and provides a Firefox plugin that makes it easier to grab snippets from pages that one browses. While Cohere and Think Link both connect an argument graph to the web, they do so in very different ways. In Cohere, a user attaches a web snippet to their idea in order to use it as evidence. By contrast, in Think Link, the main reason to connect a web snippet to an argument is to mark the snippet as contentious and encourage other readers of the snippet to look at the argument.

ClaimSpotter~\cite{Sereno2005,Sereno2004} allows one to mark up a scholarly document with logical triples (subject, verb, object) describing interesting claims that are being made in the document. This semantic information can be used to connect claims in different documents and see when a logical claim in one document contradicts another. Entity Workspace~\cite{Bier2006} does something similar for intelligence documents.

Think Link uses a relatively simple graph structure, similar to that of gIBIS~\cite{Conklink1987}, allowing a claim to support, oppose, or be related to another claim. Cohere~\cite{Shum2008} extends this by allowing one to new link types marked with pro,con,or neutral polarity Toulmin~\cite{toulmin1958} proposes a more complex graph structure, implemented that expresses warrants, data, qualifiers, and reservations. Verheij~\cite{Verheij1999} uses the Toulmin model to create an argumentation tool for lawyers.

Think Link's argument visualization is influenced by the left-to-right layout of Cohere~\cite{Shum2008}. Compendium~\cite{Selvin2001} contains a number of other visualizations of argument graphs. Mess Maps~\cite{Horn2007} present an alternative view in which an argument is divided into different sectors, each of which presents the argument from a different frame of discourse (e.g. policy maker vs industrialist vs environmentalist).

Isenmann and Reuter~\cite{Isenmann1997} identify a number of problems with the IBIS model, which they argue are reasons why it has not achieved widespread use. We believe that while the problems they observe are important when an IBIS tool is being used for conflict modelling and resolution they are less of a problem for a tool like Think Link that is designed primarily for conflict discovery. We do not expect users to use Think Link to create a detailed model of an argument and use this to reach consensus. Instead, our aim is that a user should use Think Link to discover when things they read are disputed, and easily find evidence for the other side.
\todo{Say more about this}.

When chosing an argumentation structure, there is an inherent trade-off between accurately modelling the structure of an argument and making the tool easy to use. For Think Link, we have tried to minimize the complexity of the model, and thus adopted a very simple pro/con/netural link model. The idea here is not so much to present the detailed logical structure of an argument as to show a user what sources they should look at when forming an argument for or against a claim.

% TRELLIS
% 
%  gIBIS~\cite{Conklin1987} and other IBIS~\cite{Rittel1973} such as ZEN
% 
% Cohere~\cite{Shum2008} is probably the tool most similar
% 
% 
% 
% Cohere~\cite{Shum2008}. Compendium~\cite{Selvin2001}. Cope it~\cite{Karacapilidis2001}. AIF~\cite{McGinnis2007} and ArgDF~\cite{Rahwan2007}. IBIS~\cite{Rittel1973}. gIBIS~\cite{Conklin1987}. IBIS problems~\cite{Isenmann1997}. ClaimSpotter~\cite{Sereno2005,Sereno2004}. ClaiMaker~\cite{Uren2003}. Video Annotation~\cite{Diakopoulos2008}. Collabatorium~\cite{Klein2007}, for Global Warming~\cite{Malone2007}. Lawyer argument model~\cite{Verheij1999}. Toulmin model~\cite{Toulmin1958}. Zeno~\cite{Gordon1997}. Discoursium~\cite{Yetim2007}.
% Entity Workspace~\cite{Billman2007}. 
% Mess Maps and Resolution Mapping~\cite{Horn2007}.
% TRELLIS~\cite{Chklovski2005}.  
% People should define own link types~\cite{Wang1998}.
% 
% Hypertext systems such as Notecards~\cite{Halasz1988}.

\subsection{Checking Accuracy and Bias on the Web}

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners have investigated to determine whether they are true or not. FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts.

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube presents a user with articles on the same topic that have different biases. MediaCloud applies various statistical analyses to news sources so that a reader can see when different news sources associate different words with the same topic.

Several authors have investigated ways to make Wikipedia\footnote{http://wikipedia.org} more trustworthy. WikiTrust~\cite{Adler2008} highlights passages on wikipedia based on the likelihood that another user will change that text in the future --- recent edits by untrusted editors are marked as less trustworthy than old edits by trusted editors. Wiki Dashboard~\cite{Kittur2008} presents the reader of a Wikipedia article with a visualization that shows them how it has been edited in the past and lets them see graphically how contentious the topic is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds Wikipedia edits that have been made by people with an interest in spreading misinformation (e.g. people from a company editing pages about that company).

% 
% 
% NewsCube~\cite{Park2009}.
% Wikipedia fixes Vandalism~\cite{Viegas2004}.
% Trustworthiness~\cite{Gil2006}.
% WikiTrust~\cite{Adler2008}. Wiki Dashboard~\cite{Kittur2008}.
% Wiki Scanner\footnote{http://wikiscanner.virgil.gr}.
% SourceWatch\footnote{http://sourcewatch.org}, Snopes\footnote{http://snopes.com}, FactCheck\footnote{http://factcheck.org}.

@@

Video Annotation~\cite{Diakopoulos2008}
